---
title: "Basic Research Methods"
author: "Dr. Kaung Myat Khant"
date: "`r Sys.Date()`"
output:
  ioslides_presentation:
    keep_md: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment = "",
                      warning = F,
                      message = F)
```

## Key Public Health Research Methods

-   Reviews
-   Quantitative approach 
-   Qualitative approach 
-   Mixed-method approach  

## Reviews  
-   Literature reviews
-   Systematic reviews  

## Quantitative approach  
-   produce numeric answers
-   take measurements and processed statistically
-   make prediction
-   establish relationships between the measured variables 
-   start with hypothesis or theory
-   end with deduction through analysis of collected data
-   major resource for evidence-based practice  

## Advantages and Disadvantages of Quantitative Approach  
-   Advantages  
    -   can produce objective answers
    -   can generalize the results with a good design and conduct 
-   Disadvantages
    -   may require large sample size to make inference about population
    -   focus on a narrow research question
    -   require robust study design
    
## Quantitative study designs
-   Descriptive study
    -   Cross-sectional study  
    -   Epidemiological surveys 
-   Analytic study
    -   Case control study
    -   Cohort study
-   Experimental study
    -   Randomized controlled trial
    -   Quasi experimental study
    
## Case study: quantitative research

Let's say, we've collected data of 10,000 users from dating apps such as **tinder**, **match** ,etc.

```{r startup, include=FALSE}
rm(list = ls())
set.seed(123)
data.male <- data.frame(gender = rep("male", n=100), age = sample(18:40,100,replace = T), match_age = sample(18:22, 100, replace = T) )
data.female <- data.frame(gender = rep("female",n=100), age = sample(18:40, 100, replace = T))
data.female$match_age <- data.female$age + sample(c(-3,-2,-1,0,1,2,3),100,replace = T)
data.female$match_age <- replace(data.female$match_age,
                                          data.female$match_age < 18,
                                          18)
data <- rbind(data.male, data.female)
library(tidyverse)
set.seed(111)
data <- sample_n(data, 10000, replace = T)
data <- data %>% 
   mutate(id = 1:nrow(data)) %>% 
   relocate(id, .before = everything())
```

## But the data is really messy

```{r messy, include=TRUE}
data %>% pivot_wider(id_cols = id,
                     ,names_from = gender, values_from = c(age, match_age), values_fill = 99) %>% 
  slice_head(n = 5) %>% 
  knitr::kable()
```

## So we run a few codes to tidy up

`data %>% pivot_wider(id_cols = id, names_from = gender, values_from = c(age, match_age), values_fill = 99) %>% pivot_longer(cols = -id, names_to = c(".value", "gender"), names_pattern = "(age|match_age)_(female|male)") %>% mutate(across(c(age, match_age), ~ na_if(., 99))) %>% filter(complete.cases(.))`

## And we get this tidy data and now our data has meaning

```{r tidy, include=TRUE}
data %>%
  pivot_wider(id_cols = id,
              names_from = gender, 
              values_from = c(age, match_age), 
              values_fill = 99) %>%
  pivot_longer(cols = -id,
               names_to = c(".value", "gender"),
               names_pattern = "(age|match_age)_(female|male)") %>%
  mutate(across(c(age, match_age), ~ na_if(., 99))) %>% filter(complete.cases(.)) %>% 
  slice_head(n=5) %>% knitr::kable(align = c("r","l","r","r"))
```

## We use statistics to see what we could know from our data

$$matched\_age = \alpha + \beta_1 \times age + \beta_2 \times gender$$

## And here is what we got

```{r plot, include=TRUE}
ggplot(data = data, mapping = aes(x = age, y = match_age, colour = gender))+
  geom_smooth(linewidth = 1.5,se = F)+
  scale_color_manual(values = c("pink","lightblue"))+
  labs(
    x = "Age of the dataing app users",
    y = "Matched partners'age",
    title = "Function between Age and Romantic Attraction",
    subtitle = "Men tend to date younger women,\nwhile women tend to date men who are of a similar age",
    colour = "Gender of the dating app user"
  )+
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = "wheat1", colour = "black"),
        legend.position = "right")

```

## Qualitative approach
-   produce descriptions (words)
-   explore feeling, understanding, experiences, etc
-   observe and explain human behavior
-   start with description about behavior, experience, feeling,etc
-   end with induction of a theory to explain the findings
-   process description into categories and themes 
-   study designs may be dynamic


## Advantages and disadvantages of Qualitative approach
-   Advantages
    -   can cover a broader aim and objective
    -   small sample with in-depth data is enough for understanding
    -   Themes produced can be transferred to similar context
    -   can construct theory

-   Disadvantages
    -   subjective answers generated by researchers and study participants
    -   results cannot be generalized because context is specific
    -   dynamic study design may be intensive
    
## Qualitative study designs
-   Qualitative interviews
-   Focus group research
-   Qualitative observational methods
-   Ethnography
-   Thematic analysis
-   Grounded theory
-   Nominal group technique
-   Delphi process

## Case study: Qualitative research
Here, we’ve asked the women from Reddit what they expected on their first date

## Some of their answers
-   "Getting to know each other life: hobbies, work, funny stories, personality, values (not too deep for a first date but enough to make sure we align)"
-   "I expect to be treated with courtesy and respect. I hope to get to know that person a bit better and see if we may be a good fit."
-   "Basic human decency and just getting to know each other"
-   "Many people have far too many expectations from a first date, when they should only really serve as a compatibility test. If something comes out of it, great, but never approach a first date expecting instant gratification."
-   "To spend some time together, preferably over drinks, and see if there’s chemistry and a mutual interest in getting to know each other better."

## Read, read, read and make manageable chunks
|Code|Text|
|:----:|:----|
|Compatibility|Getting a good feel of my date’s personality and values, establish if there’s basic compatibility|
|Getting to know each other|I hope to get to know that person a bit better|
|Not instant gratification|never approach a first date expecting instant gratification|
|Decent behavior|I expect to be treated with courtesy and respect|

## Results

```{r fishbone, include=TRUE, fig.align='center', fig.cap="Fishbone diagram showing women's expectation on first date"}
fishbone <- imager::load.image("fishbone.png")
plot(fishbone, axes = F)
```
  
